New Insights on the Role of Context in the Perception of a Human-like Robot

### 2015-03-17 main.tex
Reorganized the sections Design/Study/Course of the Study + rewritten several of the corresponding subsections

@@

\begin{figure}
    \centering
    \small

@@

    \caption{\small 2x2 design: the \emph{robot} vs \emph{human} condition is within
        subject, while the \emph{shallow cognitive context} vs \emph{deep
        cognitive context} is between subject. Two stimuli (\emph{``toys''}
        scene, {\bf A}, and \emph{``noise''} scene, {\bf B})
        were shown to the participants, introduced by brief verbal commands, reproduced
        here. While visually identical (see screenshots on
        figure~\ref{fig:stimuli}), the stimuli were introduced with different
        commands in the two conditions \emph{shallow} and \emph{deep cognitive
        context}.}

    \label{}
\end{figure}

Participants were made to watch the $\mathcal{R}$ and $\mathcal{H}$ interaction
videos. There were two scenarios of interaction, each for $\mathcal{H}$ and
$\mathcal{R}$. Hence, there were a total of 4 videos to be watched by each
participant. These 4 videos were replicated in 2 sets : HC and LC tasks, out of
which only one was shown to a participant. The videos for a scenario were
identical in all regards except that the length of human videos was 57 seconds
whereas it was 110 seconds for the robot videos. This difference of duration was
because of the fact that the robot usually took longer time to perform an action
as compared to human. The difference in the HC and LC videos was only of the
initial audio command that was given to the robot or human. For example, in a LC
task, the command was \textit{``Pick up the brown toy"} whereas in HC, it was
\textit{``Pick up your favorite toy"}. Otherwise all the videos had the same
architecture starting with a human voice command followed by the response from
the robot/human.

\begin{figure}
    \centering
    \subfigure[\emph{Toys} scene, robot condition]{
        \includegraphics[height=3cm]{stimulus-robot-toys}
    }
    \subfigure[\emph{Toys} scene, human condition]{
        \includegraphics[height=3cm]{stimulus-human-toys}
    }

    \subfigure[\emph{Noise} scene, robot condition]{
        \includegraphics[height=3cm]{stimulus-robot-noise}
    }
    \subfigure[\emph{Noise} scene, human condition]{
        \includegraphics[height=3cm]{stimulus-human-noise}
    }

\section{Study}

We report on a study conducted to find the relation between anthropomorphism and
gaze patterns while observing a human robot interaction.

\subsection{Variables}

\subsubsection{Independent Variables}

As stated earlier, the videos were identical in all respects but the commands
used for priming in the LC and HC scenarios. So, we had the following
independent variables.

\paragraph{High-cognitive vs Low-cognitive}

This variable was kept between subject, \ie a participant was either shown a
LC or a HC scenario, not both. So, out of the 40 participants, 22 watched the HC
tasks and 18 watched the LC tasks.

\paragraph{Human-Human vs Human-Robot Interaction}

This variable was kept within subject, \ie a participant watched both
human as well as robot videos for either LC or HC task. To avoid any order
effect among the human and robot videos for a participant, we had an equal
distribution among participants where 20 of them watched human videos before the
robot videos and the other 20 watched the videos in reverse order (robot videos
before human)

@@

Among the two scenarios, the first was one was about the robot/human picking up
a toy and the second one about pointing to the noise. As seen in figure 1(b), in
the first scenario, we had 10 AOIs: 1 for the actor's (robot/human) head, 2 for
arms (left and right), 2 for hands, 2 for legs and 1 for torso, and also 2 for
the two toys (green and brown). Similarly, as shown in figure 1(c), we had 10
AOIs for the second scenario, where the 2 AOIs for toys were replaced by two
speakers that produced sound. We fetched the gaze patterns that fall into one of
these 10 AOIs and analyzed the gaze distribution among them.

\begin{figure}
    \subfigure[$\mathcal{R}$ : Toy Scene (without AOIs)]
    {\includegraphics[width=3.3in]{stimulus-toys}\label{Toy Scene (without AOIs)}}

    \subfigure[$\mathcal{R}$ : Toy Scene (with AOIs)]
    {\includegraphics[width=3.3in]{aoi-robot}\label{Toy Scene(with AOIs)}}

    \subfigure[$\mathcal{H}$ : Sound Scene (with AOIs)]
    {\includegraphics[width=3.3in]{aoi-human}\label{Sound Scene(with AOIs)}}

    \caption{Areas of interest (AOI)}
\end{figure}

@@

Participants on an average were around 21 years of age, with a standard
deviation of 4.5. Among 40 participants, 21 were females and 19 were males.  We
tried and managed to avoid having participants from Computer Science or
Electronics background as they are generally perceived to have a lower
anthropomorphic attitude by default. As per our questionnaire responses, we
observed that the participants were not so familiar with robots and only a few
out of 40 had ever owned a robot.  It took approximately 15 minutes per
participant for one experiment session.  Each participant was invited for only
one session.

@@

\begin{figure}
    {\includegraphics[width=3.3in]{ManipulationCheck}}
    \caption{ManipulationCheck}
    \label{fig:ManipulationCheck}
\end{figure}

>>>>

This study is build as an eye-tracking experiment (mainly measuring fixation times on
various body parts) where participants watch short videos of an agent (either a
robot or a human) performing a very simple task (like picking an object), in
two different \emph{socio-cognitive contexts}. These contexts, created by priming
and/or audio cues, are designed to elicit either a shallow cognitive context
(that participant would refer as a \emph{machine-like} situation) or a deeper
cognitive context (refered as a \emph{human-like} situation).

@@

The study follows a 2x2 design, summarized in table~\ref{table:design}. Our two
independent variables are the level of socio-cognitive context (\emph{shallow
cognitive context} vs \emph{deep cognitive context}) and the nature of the
agent appearing in the stimulus (a \emph{robot}, eliciting a \emph{human-robot} interaction
situation, or a \emph{human}, eliciting a \emph{human-human} interaction
situation).

\begin{table}
    \centering
    \small

@@

    \caption{\small The study follows a 2x2 design: the \emph{robot} vs
        \emph{human} condition is within subject, while the \emph{shallow
        cognitive context} vs \emph{deep cognitive context} is between subject.
        Two stimuli (\emph{``toys''} scene, {\bf A}, and \emph{``noise''} scene,
        {\bf B}) were shown to the participants, introduced by brief verbal
        commands, reproduced in the table. While visually identical (see
        screenshots on figure~\ref{fig:stimuli}), the stimuli were introduced
        with different commands in the two conditions \emph{shallow} and
        \emph{deep cognitive
        context}.}

    \label{table:design}
\end{table}

@@

Four different video stimuli where filmed (figure~\ref{fig:stimuli}): two
different tasks (picking a stuffed animal, refered hereafter as the
\emph{Picking} task, and pointing towards a source of sound, refered as the
\emph{Sound} task) acted either by a human or a robot. Video stimuli were
realised in studio conditions. All videos followed the same simple structure: an
initial audio command (spoken by an invisible person), followed by the task
being executed.

The human actor was instructed to follow as closely as possible the actions and
attitudes of the robot (left/right glances, hesitations\ldots), while keeping a
natural, \emph{human-like} general behaviour.  Hence, the length of human videos
(57 seconds in total for the two tasks) was shorter than robot videos (110
seconds) due to the robot being usually slower in performing actions (in
particular walks) compared to human.

The audio (and audio only) of these four videos was edited to create two sets of
stimuli: one for the \emph{shallow cognitive context} condition, one for the
\emph{deep cognitive context} condition. The audio editing consisted in
inserting \emph{different commands} to initiate the tasks (reported in
table~\ref{table:design}), and, in the \emph{Sound} task, to use as sound source
either a repetitive bip (\emph{shallow cognitive context}) or the sound of a
crying baby (\emph{deep cognitive context}).

\begin{figure}
    \centering
    \subfigure[\emph{Picking} task, robot condition]{
        \includegraphics[height=3cm]{stimulus-robot-toys}
    }
    \subfigure[\emph{Picking} task, human condition]{
        \includegraphics[height=3cm]{stimulus-human-toys}
    }

    \subfigure[\emph{Sound} task, robot condition]{
        \includegraphics[height=3cm]{stimulus-robot-noise}
    }
    \subfigure[\emph{Sound} task, human condition]{
        \includegraphics[height=3cm]{stimulus-human-noise}
    }

\section{Course of the study}

@@

Participants on an average were around 21 years of age (SD=4.5). Among 40
participants, 21 were females and 19 were males.

The participants were recruited amongst students of our university. To avoid students
with a higher familiarity with robots and artificial intelligent systems,
Computer Science and Electronics curriculum were excluded. This was \textit{a
posteriori} comforted as per the questionnaire responses: no
participants\fxwarning{to be checked}
reported itself as being familiar with robots and only a few\fxwarning{how
many?} out of 40 had ever owned a robot.

It took
approximately 15 minutes per participant for one experiment session.  Each
participant was invited for only one session.

The \emph{shallow} vs \emph{deep cognitive context} condition was between
subject: Out of the 40 participants, 22 watched the \emph{deep cognitive}
tasks and 18 watched the \emph{shallow cognitive} tasks.

The \emph{robot} vs \emph{human} condition was within subject. The order of
stimuli presentation was counter-balanced over the 40 participants.

@@

\begin{figure}
    {\includegraphics[width=3.3in]{ManipulationCheck}}
    \caption{Manipulation check}
    \label{fig:ManipulationCheck}
\end{figure}

Among the two scenarios, the first was one was about the robot/human picking up
a toy and the second one about pointing to the noise. As seen in
figure~\ref{fig:aoi-toys}, in
the first scenario, we had 10 AOIs: 1 for the actor's (robot/human) head, 2 for
arms (left and right), 2 for hands, 2 for legs and 1 for torso, and also 2 for
the two toys (green and brown). Similarly, as shown in
figure~\ref{fig:aoi-noise}, we had 10
AOIs for the second scenario, where the 2 AOIs for toys were replaced by two
speakers that produced sound. We fetched the gaze patterns that fall into one of
these 10 AOIs and analyzed the gaze distribution among them.

\begin{figure}
    \centering
    \subfigure[\emph{Picking} task, robot condition]
    {\includegraphics[width=0.8\columnwidth]{aoi-robot}\label{fig:aoi-toys}}

    \subfigure[\emph{Sound} task, human condition]
    {\includegraphics[width=0.8\columnwidth]{aoi-human}\label{fig:aoi-noise}}

    \caption{Areas of interest used for the gaze analysis}
    \label{fig:aoi}
\end{figure}
